Cover letter for the original IJRR submission

### 2017-10-09 body/conclusion.tex
final changes from rev 1

% !TEX root =  ../main_tro.tex
 \section{Discussion: validity and interest of our contact planner} 
\label{sec:discussion}

@@

As demonstrated in the results section, the main interest of our method is the reduction of the algorithmic complexity of the problem, which leads to an interactive 
application. This property is critical for 
online applications with the robot and was not proposed by any of the previous contributions. Our method addresses highly constrained environments while improving the search time by orders of magnitude. This high performance is reached at the cost of some approximations that we discuss here. 
%~ In previous approaches, we identified 2 sources of high computational cost.

>>>>

% !TEX root =  ../main_tro.tex
 \section{Discussion: validity and purpose of our contact planner} 
\label{sec:discussion}

@@

As demonstrated in the results section, the main purpose of our method is the reduction of the algorithmic complexity of the problem, which leads to an interactive 
application. This property is critical for 
online applications with the robot and was not proposed by any of the previous contributions. Our method addresses highly constrained environments while improving the search time by orders of magnitude. This high performance is reached at the cost of some approximations that we discuss here. 
%~ In previous approaches, we identified 2 sources of high computational cost.

### 2017-10-09 body/equilibrium.tex
final changes from rev 1

According to Coulomb's law, the non-slipping condition is verified if all the contact forces lie in the friction cone defined by the surface.
As classically done, we linearize the friction cone in a conservative fashion with a pyramid, described by four generating rays of unit length. We choose for instance:
\begin{equation*}
\mathbf{V}_{i} = \mat{\mathbf{n}_{i} + \mu \mathbf{\boldsymbol\upgamma}_{i1} & \mathbf{n}_{i} -\mu \mathbf{\boldsymbol\upgamma}_{i1} & \mathbf{n}_{i} + \mu \mathbf{\boldsymbol\upgamma}_{i2} & \mathbf{n}_{i} - \mu \mathbf{\boldsymbol\upgamma}_{i2}}^T
\end{equation*}

>>>>

According to Coulomb's law, the non-slipping condition is verified if all the contact forces lie in the friction cone defined by the surface.
As classically done, we linearize the friction cone in a conservative fashion with a pyramid included in it, described by four generating rays of unit length. We choose for instance:
\begin{equation*}
\mathbf{V}_{i} = \mat{\mathbf{n}_{i} + \mu \mathbf{\boldsymbol\upgamma}_{i1} & \mathbf{n}_{i} -\mu \mathbf{\boldsymbol\upgamma}_{i1} & \mathbf{n}_{i} + \mu \mathbf{\boldsymbol\upgamma}_{i2} & \mathbf{n}_{i} - \mu \mathbf{\boldsymbol\upgamma}_{i2}}^T
\end{equation*}
